 

### 2021-03-08 vertical-thermal-review.Rmd
knit latest

# DISPLAY ITEMS  (limit 8) # This chunk is for auto numbering of tables/figures
#figures
fig_schematic = 1
fig_NEON_vertical =  2
#fig_NEON_differences (issue #31)
fig_leaf_T = 3
fig_treerings= 4 #not sure if we want to include one
fig_model=5

>>>>

# DISPLAY ITEMS  (limit 8) # This chunk is for auto numbering of tables/figures
#figures
fig_schematic = 1
fig_NEON_vertical =  2
fig_leaf_T = 3
fig_treerings= 4 #not sure if we want to include one
fig_model=5
